Finite-state morphological transducers for three Kypchak languages

### 2014-05-21 kipchak-lrec-2013/kipchak-paper.tex
added missing examples
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@53322 72bbbca6-d526-0410-a7d9-f06f51895060

In Kazakh, the vowels /{\qipa ɘ}/ ‹і› and /ə/ ‹ы› followed by a glide /w/ ‹у› or /j/ ‹й› are written ‹у› and ‹и›, depending on the glide; for example.  The character ‹ю› is used in turn to represent ‹й› followed by either multi-phoneme value of ‹у›.  For example, ‹қиюда› /qəjəwd{\qipa ɑ}/ `in the process of chopping down' and ‹киюде› /k{\qipa ɘ}j{\qipa ɘ}wd{\qipa i̯ɘ}/ `in the process of getting dressed' have back- and front-harmonising values, respectively, for ‹и› and ‹ю›.\footnote{Note also that the orthography suggests the presence of an additional /j/ in these words.}

>>>>

In Kazakh, the vowels /{\qipa ɘ}/ ‹і› and /ə/ ‹ы› followed by a glide /w/ ‹у› or /j/ ‹й› are written ‹у› and ‹и›, depending on the glide; e.g.\ ‹қи› /qəj/ `chop down', ‹ки› /k{\qipa ɘ}j/ `get dressed'.  The character ‹ю› is used in turn to represent ‹й› followed by either multi-phoneme value of ‹у›.  For example, ‹қиюда› /qəjəwd{\qipa ɑ}/ `in the process of chopping down' and ‹киюде› /k{\qipa ɘ}j{\qipa ɘ}wd{\qipa i̯ɘ}/ `in the process of getting dressed' have back- and front-harmonising values, respectively, for ‹и› and ‹ю›.\footnote{Note also that the orthography suggests the presence of an additional /j/ in these words.}
%би /b{\qipa ɘ}j/ `dance', қидым /qəjdəm/ `I chopped', су /səw/ `water', білу /b{\qipa ɘ}l{\qipa ɘ}w/ `knowing'
